---
title: "Pancreatobiliary Pathology Society Journal Watch"
date: "Last Update on `r format(Sys.Date())`"
subtitle: Recent Articles that will be Selected
---

Website under Construction!

Will add  
- logo  
- consider using distill  



```{r}
Sys.time()
```


```{r global_options, include=FALSE}
# knitr::opts_chunk$set(cache = TRUE)
```



```{r search PubMed, cache=FALSE}
source(file = "R/loadLibrary.R")
source(file = "searchPubMed.R")
source(file = "R/removeDuplicates.R")
```


<style type="text/css">

h1{
  text-align: center;
}
h2{
  text-align: center;
}
h3{
  text-align: center;
}
h4{
  text-align: center;
}
h4.date{
  text-align: center;
}

</style>


---

# PBPath Journal Watch Articles {.tabset .tabset-fade .tabset-pills #pbpath_jw}




---

**Welcome to the PBPath Journal Watch!** 



This bi-monthly journal watch features exciting recently published pancreas and biliary pathology articles that will provide up to date medical knowledge in our field. These articles will be showcased in several convenient categories, including surgical pathology, cytopathology, molecular pathology, pancreas, gallbladder, bile ducts, and ampulla among others. The articles in each category are in no particular order. See the list of journals we search regularly [here](http://pbpath.org/pbpath-journal-watch/). Previous months’ issues may be found in our *[archive](http://pbpath.org/journal-watch-archive/)* and you may see [drafts of the upcoming issue here](http://pbpath.org/journal-watch-upcoming-issue/).  

We encourage members to actively participate by recommending new articles and providing feedback using the [forms provided below.](#feedback){target="_self"}  

**We hope that you will enjoy the new PBPath Journal Watch!**


<!-- ```{r PubMed Link, include=FALSE, cache=FALSE} -->
<!-- PMID_all <- dplyr::bind_rows(pancreas_recent_PMID, -->
<!--                              gallbladder_recent_PMID, -->
<!--                              bileduct_recent_PMID, -->
<!--                              ampulla_recent_PMID, -->
<!--                              previousJW_PMID -->
<!-- ) %>%  -->
<!--   dplyr::arrange(dplyr::desc(PMID)) %>%  -->
<!--   head(., n = 100) -->


<!-- PMIDs <- PMID_all$PMID %>%  -->
<!-- t() %>% -->
<!-- paste0("[uid] OR ", collapse = "") # add OR between PMID List -->

<!-- PMIDs <- gsub(" OR $", "" , PMIDs) # to remove last OR -->

<!-- Recent_PubMed_Link <- paste0("To see these selected articles in <a href = 'https://www.ncbi.nlm.nih.gov/pubmed/?term=",PMIDs,"'> PubMed click here </a>") -->

<!-- write(x = Recent_PubMed_Link, -->
<!--       file = here::here("data","Recent_PubMed_Link.txt")) -->

<!-- ``` -->



<!-- ```{r Lens Link, include=FALSE, cache=FALSE} -->
<!-- PMID_Lens <- paste0("pmid:",PMID_all$PMID,"%20OR%20" ) %>%  -->
<!--   t() %>%  -->
<!--   paste0(collapse = "") -->

<!-- PMID_Lens <- gsub("%20OR%20$", "" , PMID_Lens) -->

<!-- Recent_Lens_Link <- paste0("To see these selected articles in <a href = 'https://www.lens.org/lens/scholar/search/results?q=",PMID_Lens,"&toYear=2020&fromYear=1950&dateFilterField=year_published&filterMap=%7B%7D&preview=true'> Lens.org click here </a>") -->

<!-- write(x = Recent_Lens_Link, -->
<!--       file = here::here("data","Recent_Lens_Link.txt")) -->

<!-- ``` -->


<!-- <details> <summary> -->
<!-- Click here to see these articles and graphical summaries in other databases -->
<!-- </summary> -->

<!-- The *journal watch* articles are collected in [zenodo](https://doi.org/10.5281/zenodo.3635440) and [OSF](https://osf.io/3d67y/).   -->
<!-- [![DOI](https://zenodo.org/badge/DOI/10.5281/zenodo.3635440.svg)](https://doi.org/10.5281/zenodo.3635440)   -->


<!-- "r Recent_PubMed_Link" -->


<!-- "r Recent_Lens_Link" -->

<!-- </details> -->


<!-- --- -->

<!-- ```{r run all Rmd without knit, eval=FALSE, include=FALSE} -->
<!-- source_rmd <- function(rmd_file){ -->
<!--   knitr::knit(rmd_file, output = tempfile(), envir = globalenv()) -->
<!-- } -->

<!-- list_of_Rmd <- list.files(path = here::here(), -->
<!--                           pattern = "Recent.Rmd", -->
<!--                           full.names = TRUE) -->

<!-- purrr::map(.x = list_of_Rmd, .f = source_rmd) -->

<!-- # purrr::walk(.x = here::here("", list_of_Rmd), .f = source_rmd) -->
<!-- ``` -->

<!-- ```{r forcegit, eval=FALSE, include=FALSE} -->
<!-- # gitUpdateCommitPush -->
<!-- CommitMessage <- paste("updated on ", Sys.time(), sep = "") -->
<!-- wd <- getwd() -->
<!-- gitCommand <- paste("cd ", wd, " \n git add . \n git commit --message '", CommitMessage, "' \n git push origin master \n", sep = "") -->
<!-- system(command = gitCommand, intern = TRUE) -->
<!-- ``` -->


\pagebreak




## Pancreas {#pancreas}


---

<a href="#top" target="_self">Back to top</a>

---

\pagebreak



## Gallbladder {#gallbladder}





---

<a href="#top" target="_self">Back to top</a>

---

\pagebreak


## Bile Duct {#bileduct}



---

<a href="#top" target="_self">Back to top</a>

---

\pagebreak

## Ampulla {#ampulla}



---

<a href="#top" target="_self">Back to top</a>

---

\pagebreak

