---
title: "PBPath Journal Watch"
output: html_document
---


---

# PBPath Journal Watch Articles {.tabset .tabset-fade .tabset-pills #pbpath_jw}

---

\pagebreak


## Pancreas {#pancreas}

---


`r paste(knitr::knit(text = out_pancreas), collapse = '\n\n\n')`


```{r df_pancreas2}
df_pancreas2 <- readr::read_csv(file = "data/pancreasarticles.txt",
                               col_names = TRUE)
df_pancreas2[["PMID"]] <- as.character(df_pancreas2[["PMID"]])

```

```{r df_pancreas2 table, layout="l-body-outset"}
rmarkdown::paged_table(df_pancreas2)
```





<a href="#top" target="_self">Back to top</a>

---

\pagebreak



## Gallbladder {#gallbladder}

---

`r paste(knitr::knit(text = out_gallbladder), collapse = '\n\n\n')`


```{r df_gb2}
df_gb2 <- readr::read_csv(file = "data/gallbladderarticles.txt",
                          col_names = TRUE)
df_gb2[["PMID"]] <- as.character(df_gb2[["PMID"]])

```

```{r df_gb2 table, layout="l-body-outset"}
rmarkdown::paged_table(df_gb2)
```





<a href="#top" target="_self">Back to top</a>

---

\pagebreak


## Bile Duct {#bileduct}

---


`r paste(knitr::knit(text = out_bileduct), collapse = '\n\n\n')`


```{r df_bd2}
df_bd2 <- readr::read_csv(file = "data/bileductarticles.txt",
                         col_names = TRUE)
df_bd2[["PMID"]] <- as.character(df_bd2[["PMID"]])

```

```{r df_bd2 table, layout="l-body-outset"}
rmarkdown::paged_table(df_bd2)
```




<a href="#top" target="_self">Back to top</a>

---

\pagebreak


## Ampulla {#ampulla}

---


`r paste(knitr::knit(text = out_ampulla), collapse = '\n\n\n')`


```{r df_ampulla2}
df_ampulla2 <- readr::read_csv(file = "data/ampullaarticles.txt",
                               col_names = TRUE)
df_ampulla2[["PMID"]] <- as.character(df_ampulla2[["PMID"]])

```

```{r df_ampulla2 table, layout="l-body-outset"}
rmarkdown::paged_table(df_ampulla2)
```






<a href="#top" target="_self">Back to top</a>

---

\pagebreak

